Safe Transferable Regions

### 2016-10-04 paper/typeinference-proofs.tex
minor fixes

Invariants and other points:
\begin{itemize}
  \item Every predicate variable has a single domain-constraint.
  \item Progress: Every region-variable will be unified with some constant.
  \item Notation: should we use a different notation to distinguish a validity constraint
    from actual entailment?
\end{itemize}

>>>>

Invariants, other points, and to-dos:
\begin{itemize}
  \item use of a set to represent conjunctions
  \item equality is shorthand for two inequalities
  \item unify notation for substitution
  \item substitution required in correctness theorem as well
  \item use of alpha-renaming, and its use to discharge not-in contraints;
also, incorporate this into first stage rather than second (in Fig. 7).
  \item Modify CSP definition to be same as preceding; we can define the $\Delta$s 
    as auxiliary notation
  \item Note that we can also clarify that the well-formedness constraints are
    syntactic sugar from basic set constraints
  \item Every predicate variable has a single domain-constraint.
  \item Prove: Progress: Every region-variable will be unified with some constant.
  \item Notation: should we use a different notation to distinguish a validity constraint
    from actual entailment?
  \item Proof by relating proof-trees with constraint-generation trees; each can
    be constructed from the other; inductive lemma is as earlier
\end{itemize}
